---
title: "Welcome to the `ggplot2` graph gallery!"
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
    smooth-scroll: true
    code-fold: true
    code-summary: "View code"
    code-overflow: wrap
    highlight-style: arrow
    
---


This Quarto website contains a series of graphs composed in `ggplot2`. Install `ggplot2` using the code below:

```{r}
#| label: ggp2-pkg
#| eval: false
#| echo: true
install.packages("ggplot2")
library(ggplot2)
```

Or install it as part of the `tidyverse`:

```{r}
#| label: tidyverse-pkg
#| eval: false
#| echo: true
install.packages("tidyverse")
library(tidyverse)
```

## Graph Packages

Most of the graphs in this gallery can be built using on of `ggplot2` 's many `geom_*` functions. If a graph requires additional `geom`s or functions, the development version for these packages have been listed.

## Galleries

The graphs have been broken into separate categories:

### Univariate Graphs

The following graphs are used to display **single variable** **distributions**:

-   [ ] Bar Graphs

-   [ ] Histograms

-   [ ] Frequency Polygons

-   [ ] Dot-Plots

-   [ ] Density Plots

-   [ ] Violin Plots

-   [ ] Box-Plots

### Comparing Distributions

These graphs can be used to compare **multiple variable distributions:**

-   [ ] Overlapping Histograms

-   [ ] Overlapping Frequency Polygons

-   [ ] Overlapping Dot-Plots

-   [ ] Bee-swarm Plots

    -   [`ggbeeswarm` package](https://github.com/eclarke/ggbeeswarm)

        ```{r}
        #| eval: false
        #| echo: true
        # Bee-swarm Plots
        devtools::install_github("eclarke/ggbeeswarm")
        library(ggbeeswarm)
        ```

-   [ ] Overlapping Densities

-   [ ] Ridgeline Plots

    -   [`ggridges` package](https://wilkelab.org/ggridges/)

        ```{r}
        #| eval: false
        #| echo: true
        # Ridgeline plots 
        devtools::install_github("wilkelab/ggridges")
        library(ggridges)
        ```

-   [ ] Box-plots

-   [ ] Violin plots

-   [ ] *Rain-cloud plots*

### Comparing Amounts

The following graphs are used to display **amounts**:

-   [ ] Bar-graphs

-   [x] Grouped Bar-graphs

-   [ ] Stacked Bar-graphs

-   [ ] *Dot/point plots*

    -   We cover [dot-plots](https://mjfrigaard.github.io/ggp2-graph-gallery/slides/distributions.html#/dot-plots) above in the distributions section.

-   [ ] Waffle Charts

    -   [`ggwaffle` package](https://liamgilbey.github.io/ggwaffle/)

        ```{r}
        #| eval: false
        #| echo: true
        # Waffle Charts
        devtools::install_github("liamgilbey/ggwaffle")
        library(ggwaffle)
        ```

### Comparing Proportions

The following graphs are used to compare **proportions**:

-   [ ] Pie Charts

    -   [`ggpubr` package](https://rpkgs.datanovia.com/ggpubr/)

        ```{r}
        #| eval: false
        #| echo: true
        # Pie Charts 
        devtools::install_github("kassambara/ggpubr")
        library(ggpubr)
        ```

-   [ ] Diverging Bar-graphs

    -   Horizontal
    -   Vertical

-   [ ] Stacked-densities

-   [ ] Mosaic Plots

    -   [`ggmosaic` package](https://haleyjeppson.github.io/ggmosaic/)

        ```{r}
        #| eval: false
        #| echo: true
        # Mosaic Charts 
        devtools::install_github("haleyjeppson/ggmosaic")
        library(ggmosaic)
        ```

-   [ ] Treemaps

    -   [`treemapify` package](https://wilkox.org/treemapify/)

        ```{r}
        #| eval: false
        #| echo: true
        # Treemaps
        devtools::install_github("wilkox/treemapify")
        library(treemapify)
        ```

-   [ ] *Parallel Sets*

### Relationships

The following graphs are used to display relationships between two (or more) variables:

-   [ ] Scatter Plots

-   [ ] Grouped Scatter plots

-   [ ] Bubble Charts

-   [ ] Grouped Bubble Charts

-   [ ] Alluvial Charts

    -   [ggalluvial package](https://corybrunson.github.io/ggalluvial/)

        ```{r}
        #| eval: false
        #| echo: true
        # Alluvial charts
        devtools::install_github("corybrunson/ggalluvial")
        library(ggalluvial)
        ```

-   [ ] Bump Charts

    -   [ggbump package](https://github.com/davidsjoberg/ggbump)

        ```{r}
        #| eval: false
        #| echo: true
        # Bump charts
        devtools::install_github("davidsjoberg/ggbump")
        library(ggbump)
        ```

-   [ ] Slope-graphs

-   [ ] *Density Contours*

-   [ ] *2D Bins*

-   [ ] *Hex Bins*

-   [ ] *Correlograms*

## Data

The following datasets have been used to create the graphs:

```{r}
#| label: palmer-penguins
#| eval: false
#| echo: true

```
