---
title: "Welcome to the `ggplot2` graph gallery!"
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
    smooth-scroll: true
    code-fold: true
    code-summary: "View code"
    code-overflow: wrap
    highlight-style: arrow
    
---


This Quarto website contains a series of graphs composed in `ggplot2`. Install `ggplot2` using the code below:

```{r}
#| label: ggp2-pkg
#| eval: false
#| echo: true
install.packages("ggplot2")
library(ggplot2)
```

Or install it as part of the `tidyverse`:

```{r}
#| label: tidyverse-pkg
#| eval: false
#| echo: true
install.packages("tidyverse")
library(tidyverse)
```

## Graph Packages

Most of the graphs in this gallery can be built using on of `ggplot2` 's many `geom_*` functions. If a graph requires additional `geom`s or functions, the development version for these packages have been listed.

## Galleries

The graphs have been broken into separate categories:

### Univariate Graphs

The following graphs are used to display **single variable** **distributions**:

-   [x] [Bar Graphs](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#bar-graphs)

-   [x] [Histograms](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#histograms)

-   [x] [Frequency Polygons](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#frequency-polygons)

-   [x] [Dot-Plots](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#dot-plots)

-   [x] [Density Plots](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#density-plots)

-   [x] [Violin Plots](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#violin-plots)

-   [x] [Box-Plots](https://mjfrigaard.github.io/ggp2-gallery/univariate.html#box-plots)

### Comparing Amounts

The following graphs are used to display **amounts**:

-   [x] [Grouped column-graphs](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#grouped-column-graphs)

-   [x] [Summarized column-graphs](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#summarized-column-graphs)

-   [x] [Overlapping bar-graphs](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#overlapping-bar-graphs)

-   [x] [Side-to-side ("dodge") bar-graphs](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#side-to-side-bar-graphs)

-   [x] [Side-to-side ("dodge2") bar-graphs](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#dodge2-bar-graphs)

-   [x] [Heatmaps](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#heatmaps)

-   [x] [Waffle charts](https://mjfrigaard.github.io/ggp2-gallery/amounts.html#waffle-chart)

    -   [`ggwaffle` package](https://liamgilbey.github.io/ggwaffle/)

        ```{r}
        #| eval: false
        #| echo: true
        # Waffle Charts
        devtools::install_github("liamgilbey/ggwaffle")
        library(ggwaffle)
        ```

### Comparing Proportions

The following graphs are used to compare **proportions**:

-   [x] [Pie Charts](https://mjfrigaard.github.io/ggp2-gallery/proportions.html#pie-charts)

    -   [`ggpubr` package](https://rpkgs.datanovia.com/ggpubr/)

        ```{r}
        #| eval: false
        #| echo: true
        # Pie Charts 
        devtools::install_github("kassambara/ggpubr")
        library(ggpubr)
        ```

-   [x] [Diverging Bar-graphs](https://mjfrigaard.github.io/ggp2-gallery/proportions.html#diverging-bar-graphs)

  -   [x] [Vertical](https://mjfrigaard.github.io/ggp2-gallery/proportions.html#diverging-bar-graphs-vertical)

-   [x] [Stacked-densities](https://mjfrigaard.github.io/ggp2-gallery/proportions.html#stacked-or-filled-density-graphs)

-   [x] [Mosaic Plots](https://mjfrigaard.github.io/ggp2-gallery/proportions.html#mosaic-plot)

    -   [`ggmosaic` package](https://haleyjeppson.github.io/ggmosaic/)

        ```{r}
        #| eval: false
        #| echo: true
        # Mosaic Charts 
        devtools::install_github("haleyjeppson/ggmosaic")
        library(ggmosaic)
        ```

-   [x] [Treemaps](https://mjfrigaard.github.io/ggp2-gallery/proportions.html#treemaps)

    -   [`treemapify` package](https://wilkox.org/treemapify/)

        ```{r}
        #| eval: false
        #| echo: true
        # Treemaps
        devtools::install_github("wilkox/treemapify")
        library(treemapify)
        ```

-   [ ] *Parallel Sets*


### Comparing Distributions

These graphs can be used to compare **multiple variable distributions:**

-   [x] [Overlapping Histograms](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#overlapping-histogram)

-   [x] [Overlapping Frequency Polygons](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#overlapping-frequency-polygons)

-   [x] [Overlapping Dot-Plots](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#overlapping-dot-plots)

-   [x] [Bee-swarm Plots](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#bee-swarm-plots)

    -   [`ggbeeswarm` package](https://github.com/eclarke/ggbeeswarm)

        ```{r}
        #| eval: false
        #| echo: true
        # Bee-swarm Plots
        devtools::install_github("eclarke/ggbeeswarm")
        library(ggbeeswarm)
        ```

-   [x] [Overlapping Densities](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#overlapping-or-stacked-density-plots)

-   [x] [Ridgeline Plots](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#ridgeline-plots)

    -   [`ggridges` package](https://wilkelab.org/ggridges/)

        ```{r}
        #| eval: false
        #| echo: true
        # Ridgeline plots 
        devtools::install_github("wilkelab/ggridges")
        library(ggridges)
        ```

-   [x] [Grouped Box-plots](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#grouped-box-plots)

-   [x] [Violin plots](https://mjfrigaard.github.io/ggp2-gallery/distributions.html#grouped-violin-plots)

-   [ ] *Rain-cloud plots*



### Relationships

The following graphs are used to display relationships between two (or more) variables:

-   [x] [Scatter plots](https://mjfrigaard.github.io/ggp2-gallery/relationships.html#scatter-plot)

-   [x] [Grouped scatter plots](https://mjfrigaard.github.io/ggp2-gallery/relationships.html#grouped-scatter-plot)

-   [x] [Bubble charts](https://mjfrigaard.github.io/ggp2-gallery/relationships.html#bubble-chart)

-   [x] [Grouped bubble charts](https://mjfrigaard.github.io/ggp2-gallery/relationships.html#grouped-bubble-chart)

-   [x] [Alluvial charts](https://mjfrigaard.github.io/ggp2-gallery/relationships.html#alluvial-graphs)

    -   [ggalluvial package](https://corybrunson.github.io/ggalluvial/)

        ```{r}
        #| eval: false
        #| echo: true
        # Alluvial charts
        devtools::install_github("corybrunson/ggalluvial")
        library(ggalluvial)
        ```

-   [x] [Bump charts](https://mjfrigaard.github.io/ggp2-gallery/relationships.html#bump-chart)

    -   [ggbump package](https://github.com/davidsjoberg/ggbump)

        ```{r}
        #| eval: false
        #| echo: true
        # Bump charts
        devtools::install_github("davidsjoberg/ggbump")
        library(ggbump)
        ```

-   [ ] *Slope-graphs*

-   [ ] *Density Contours*

-   [ ] *2D Bins*

-   [ ] *Hex Bins*

-   [ ] *Correlograms*

## Data

The following datasets have been used to create the graphs:

```{r}
#| label: palmer-penguins
#| eval: false
#| echo: true

```
