---
title: "ggplot2 graph gallery"
author: "Relationships"
format:
  revealjs:
    height: 900
    width: 1600
    code-line-numbers: true
    theme: [night, slides.scss]
    background-transition: fade
    transition: slide
    transition-speed: fast
    highlight-style: ayu-mirage
    
code-link: true
execute:
  echo: true
  freeze: auto
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
library(xml2)
library(reactable)
library(ggalluvial)
# options ----
options(
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
# ggplot2 theme ----
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
# funs ----
ds538 <- readr::read_rds("data/ds538.rds")
# movies_data ----
movies_data <- readr::read_rds("data/movies_data.rds")
```

# Load packages

<br>


:::: columns
::: {.column width="49%"}

Data packages:

<br>

::: {style="font-size: 0.80em; color:"}
```{r}
#| eval: true
#| echo: true
#| label: packages-data
library(tidyverse)
# install.packages('fivethirtyeightdata', 
# repos = 'https://fivethirtyeightdata.github.io/drat/', 
# type = 'source')
library(scales)
library(kableExtra)
library(palmerpenguins)
library(fivethirtyeight)
library(ggplot2movies)
```
:::
:::

::: {.column width="2%"}
:::

::: {.column width="49%"}

Graph packages:

<br>

::: {style="font-size: 0.80em; color:"}
```{r}
#| eval: true
#| echo: true
#| label: packages-graphs
# install.packages("devtools")
# devtools::install_github("eclarke/ggbeeswarm")
library(ggbeeswarm)
# devtools::install_github("wilkelab/ggridges")
library(ggridges)
```
:::
:::
::::


# palmerpenguins

<br>

*You can learn more about the `penguins` data on the [package website](https://allisonhorst.github.io/palmerpenguins/)*

<br>

:::: columns
::: {.column width="38%"}
```{r}
#| eval: false
#| echo: true
#| label: penguins
penguins <- palmerpenguins::penguins
glimpse(penguins)
```
:::

::: {.column width="2%"}
:::

::: {.column width="60%"}
```{r}
#| eval: true
#| echo: false
#| label: penguins-glimpse
penguins <- palmerpenguins::penguins
glimpse(penguins, 50)
```
:::
::::

# fivethirtyeight

<br>

*All datasets from the [`fivethirtyeight` package](https://fivethirtyeight-r.netlify.app/) are listed below with descriptions*

<br>

Access them using: 

```{r}
#| label: fivethirtyeight-namespace
#| eval: false
#| echo: true
fivethirtyeight::
```

```{r}
#| label: fivethirtyeight-kable
#| eval: true
#| echo: false
#| message: false
#| warning: false
kableExtra::kable_material_dark(
  kable_input = knitr::kable(
    head(ds538)
    ), font_size = 25
  )
```

# ggplot2movies

<br>

*We're using `movies_data` (derived version of the [`ggplot2movies::movies`](https://github.com/hadley/ggplot2movies))*

<br>

::: columns
::: {.column width="38%"}
```{r movies_data}
#| eval: false
#| echo: true
#| label: movies_data
#| message: false
#| warning: false
glimpse(movies_data)
```
:::

::: {.column width="2%"}

:::

::: {.column width="60%"}
```{r glimpse-movies_data, echo=FALSE}
#| eval: true
#| echo: false
#| label: movies_data-glimpse
#| message: false
#| warning: false
glimpse(movies_data, 50)
```
:::
:::

# RELATIONSHIPS

<br>

::: {.fragment fragment-index=1}
Trends,  
:::

::: {.fragment fragment-index=2}
correlations,
:::

::: {.fragment fragment-index=3}
and connections
:::

::: {.fragment fragment-index=4}
::: {style="font-size: 1.00em; color: #ffac00;"}
with `ggplot2`
:::
:::

# SCATTER PLOT

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***Should I use this graph?***
:::

<br>

. . .

<br>

Scatter plots are used to display two continuous variables.

. . .

<br>

If one of the continuous variables is assumed to affect the other (i.e., `outcome` vs. `predictor`), place the `outcome` on the `y` axis and the `predictor` on the `x` axis.


## SCATTER PLOT

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::


::: {style="font-size: 0.80em;"}
The `penguins` data
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_scatter
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_scatter
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.75em;"}

1. Create labels

2. Map `bill_length_mm` to the `x` axis

3. Map `flipper_length_mm` to the `y` axis

4. Add `geom_point()`  
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_scatter
#| code-line-numbers: "1-11|1-3|6-7|8|10-11"
#| eval: false
#| echo: true 

labs_scatter <- labs(
  title = "Bill Length vs. Flipper Length",
  x = "Bill Length (mm)", y = "Flipper length (mm)")
ggp2_scatter <- penguins |>
  ggplot(
    aes(x = bill_length_mm, 
      y = flipper_length_mm)) +
  geom_point()

ggp2_scatter + 
  labs_scatter
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

If multiple points occupy the same value position, use transparency (`alpha`) to improve visibility.

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_scatter
#| eval: true
#| echo: false

# create graph layers 
labs_scatter <- labs(title = "Bill Length vs. Flipper Length",
                      x = "Bill Length (mm)", y = "Flipper length (mm)")

ggp2_scatter <- penguins |> 
  ggplot(aes(x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point() 

ggp2_scatter + 
  labs_scatter
```
:::
::::


::::::

# GROUPED SCATTER PLOT

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***Should I use this graph?***
:::

<br>

. . .

<br>

To display the relationship between **two** continuous variables across a third categorical variable...

. . .

<br>

...use color to distinguish between categorical levels across the two continuous variable. 

## GROUPED SCATTER PLOT

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
The `penguins` data.
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_grp_scatter
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_grp_scatter
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.75em;"}
1. Create labels

2. Map `bill_length_mm` to the `x` axis 

3. Map `flipper_length_mm` to the `y` axis  

4. Map `species` to `color` inside the `geom_point()`
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_grp_scatter
#| code-line-numbers: "1-13|1-4|8-9|10|12-13"
#| eval: false
#| echo: true 

labs_grp_scatter <- labs(
  title = "Bill Length vs. Flipper Length",
  x = "Bill Length (mm)", y = "Flipper length (mm)", 
  color = "Penguin species")

ggp2_grp_scatter <- penguins |> 
  ggplot(
    aes(x = bill_length_mm, 
        y = flipper_length_mm)) + 
  geom_point(aes(color = species)) 

ggp2_grp_scatter + 
  labs_grp_scatter
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

Adjust over-plotting with transparency (`alpha`)

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_grp_scatter
#| eval: true
#| echo: false

labs_grp_scatter <- labs(title = "Bill Length vs. Flipper Length",
                      x = "Bill Length (mm)", y = "Flipper length (mm)", 
                      color = "Penguin species")

ggp2_grp_scatter <- penguins |> 
  ggplot(aes(x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point(aes(color = species)) 

ggp2_grp_scatter + 
  labs_grp_scatter
```
:::
::::


::::::



# BUBBLE CHART

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***Should I use this graph?***
:::

<br>

. . .

<br>

Bubble graphs display relationships between three continuous variables. 

. . .

<br>

The position on the `x` and `y` axis illustrates the relationship between the first two, and the `size` of the point (i.e., bubble) conveys the value of the third. 

## BUBBLE CHART

:::::: panel-tabset

### Code

:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
The `penguins` data  
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_bubble
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_bubble
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::

***

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.70em;"}
1. Create labels

2. Map `bill_length_mm` to `x` axis
:::


:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.70em;"}

3. Map `flipper_length_mm` to `y` axis 

4. Map `body_mass_g` to `size`  

5. Set `alpha` to `1/3`  

6. Add `scale_size()`, set the `range` to `c(0.1, 10)` and `name` to `"Body Mass (g)"`
:::

::: {style="font-size: 0.80em;"}
```{r}
#| label: graph_code_bubble
#| code-line-numbers: "1-15|1-4|7-8|9|10-11|13-14"
#| eval: false
#| echo: true 

labs_bubble <- labs(
  title = "Bill Length vs. Flipper Length",
  x = "Bill Length (mm)", y = "Flipper length (mm)", 
  size = "Body Mass (g)")

ggp2_bubble <- penguins |> 
  ggplot(
    aes(x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point(aes(size = body_mass_g), alpha = 1/3) + 
  scale_size(range = c(.1, 10), 
             name = "Body Mass (g)")

ggp2_bubble + 
  labs_bubble
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

Once again, transparency (`alpha`) can be used to handle over-plotting

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_bubble
#| eval: true
#| echo: false

labs_bubble <- labs(
  title = "Bill Length vs. Flipper Length",
  x = "Bill Length (mm)", y = "Flipper length (mm)", 
  size = "Body Mass (g)")

ggp2_bubble <- penguins |> 
  ggplot(aes(x = bill_length_mm, 
             y = flipper_length_mm)) + 
  geom_point(aes(size = body_mass_g), 
             alpha = 1/3) + 
  scale_size(range = c(.1, 10), 
             name = "Body Mass (g)")

ggp2_bubble + 
  labs_bubble
```
:::
::::


::::::

# GROUPED BUBBLE CHART

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***Should I use this graph?***
:::

<br>

. . .

<br>

In addition to size, the grouped bubble graph uses color to display differences across categorical levels.

## GROUPED BUBBLE CHART

:::::: panel-tabset

### Code

:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.70em;"}
The `penguins` data 
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_grp_bubble
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_grp_bubble
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::

***

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.65em;"}
1. Create labels

2. Map `bill_length_mm` to the `x` axis and  `flipper_length_mm` to the `y` axis  
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.65em;"}

3. Inside `geom_point()`  
    - map `body_mass_g` to `size` and `species` to `fill`  
    - set the `alpha` to `2/3`, shape to `21`, and `color` to `"black"`  
4. In the `scale_size()`  
    - set `range` to `c(.04, 8)` and `name` to `"Body Mass (g)"` 
  
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_grp_bubble
#| code-line-numbers: "1-15|1-4|7-8|9-10|11|12|14-15"
#| eval: false
#| echo: true 

labs_grp_bubble <- labs(
  title = "Bill Length vs. Flipper Length",
  x = "Bill Length (mm)", y = "Flipper length (mm)", 
  size = "Body Mass (g)")

ggp2_grp_bubble <- penguins |> 
  ggplot(aes(
    x = bill_length_mm, y = flipper_length_mm)) + 
  geom_point(
    aes(size = body_mass_g, fill = species), 
        alpha = 2/3, shape = 21, color = "black") + 
  scale_size(range = c(.04, 8), name = "Body Mass (g)") 

ggp2_grp_bubble + 
  labs_grp_bubble
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}


:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_grp_bubble
#| eval: true
#| echo: false

labs_grp_bubble <- labs(
  title = "Bill Length vs. Flipper Length",
  x = "Bill Length (mm)", y = "Flipper length (mm)", 
  size = "Body Mass (g)")

ggp2_grp_bubble <- penguins |> 
  ggplot(aes(
    x = bill_length_mm, 
    y = flipper_length_mm)) + 
  geom_point(
    aes(size = body_mass_g, 
        fill = species), 
          alpha = 2/3,
          shape = 21, 
          color = "black") + 
  scale_size(range = c(.04, 8), 
             name = "Body Mass (g)") 

ggp2_grp_bubble + 
  labs_grp_bubble
```
:::
::::


::::::



# ALLUVIAL GRAPHS

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***Should I use this graph?***
:::

<br>

. . .

<br>

An alluvial graph displays the changes in composition or flow over time or across multiple categories. 

. . .

<br>

We can build bump charts in `ggplot2` with the [`ggalluvial` package:](https://corybrunson.github.io/ggalluvial/)  

```{r inst-ggalluvial}
#| eval: false
devtools::install_github("corybrunson/ggalluvial")
library(ggalluvial)
```


## ALLUVIAL GRAPH (WIDE FORM)

:::::: panel-tabset

### Code

:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.70em;"}

Below we create a wide example of the `penguins` data (as `peng_wide`)
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_alluvial
#| eval: false
peng_wide <- penguins |> 
  drop_na() |> 
  count(year, island, sex, species) |> 
  mutate(year = factor(year)) |> 
  rename(freq = n)
glimpse(peng_wide)
```

```{r}
#| label: data_run_alluvial
#| eval: true
#| echo: false 
peng_wide <- penguins |> 
  drop_na() |> 
  count(year, island, sex, species) |> 
  mutate(year = factor(year)) |> 
  rename(freq = n)
glimpse(peng_wide, 50)
```
:::

***

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.65em;"}
1. Create labels (with `ggtitle()`, `ylab()`, and `labs()`)
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.65em;"}

3. Add `scale_x_discrete()` with the `limits` set to `"Year"`, `"Island"` and `"Species"`, and `expand` to `0.1` and `0.07`

4. Add `geom_alluvium()` with `fill` set to the `sex` variable and `geom_stratum()`

5. Add `geom_text()`, with `stat` set to `stratum` and label set to `after_stat(stratum)` (*inside* `aes()`) 

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: graph_code_alluvial
#| code-line-numbers: "1-15|1-4|7-8|9-11|12|13|14-15|17-20"
#| eval: false
#| echo: true 
labs_alluvial <- ggtitle(label = "Palmer Penguins", 
    subtitle = "Stratified by year, island and species")
labs_alluvial_y <- ylab("Frequency") 
labs_alluvial_fill <- labs(fill = "Sex")

ggp2_alluvial_w <- ggplot(data = peng_wide,
  aes(axis1 = year, axis2 = island,
      axis3 = species, y = freq)) +
  scale_x_discrete(
    limits = c("Year", "Island", "Species"),
    expand = c(0.1, 0.07)) +
  geom_alluvium(aes(fill = sex)) +
  geom_stratum() +
  geom_text(stat = "stratum", 
    aes(label = after_stat(stratum)))

ggp2_alluvial_w + 
  labs_alluvial + 
  labs_alluvial_y + 
  labs_alluvial_fill
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

The `ggalluvial` functions can handle wide or long data. 

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_alluvial
#| eval: true
#| echo: false

# convert to wide
peng_wide <- penguins |> 
  drop_na() |> 
  count(year, island, sex, species) |> 
  mutate(year = factor(year)) |> 
  rename(freq = n)

# labels
labs_alluvial <- ggtitle(label = "Palmer Penguins", 
    subtitle = "Stratified by year, island and species")
labs_alluvial_y <- ylab("Frequency") 
labs_alluvial_fill <- labs(fill = "Sex")

# plot with wide data
ggp2_alluvial_w <- ggplot(data = peng_wide,
  aes(axis1 = year,
      axis2 = island,
      axis3 = species,
      y = freq)) +
  scale_x_discrete(
    limits = c("Year", "Island", "Species"),
    expand = c(0.1, .07)) +
  geom_alluvium(aes(fill = sex)) +
  geom_stratum() +
  geom_text(stat = "stratum", 
    aes(label = after_stat(stratum)))

ggp2_alluvial_w + 
  labs_alluvial + 
  labs_alluvial_y + 
  labs_alluvial_fill
```
:::
::::


::::::

## ALLUVIAL GRAPH (LODES FORM)

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.70em;"}
Below we create `peng_lodes` from the `penguins` dataset using the   `to_lodes_form()` from the `ggalluvial` package.
:::

::: {style="font-size: 0.70em;"}
```{r}
#| label: data_show_alluvial_lf
#| eval: false
peng_lodes <- penguins |> 
  select(Year = year, Island = island, 
         Species = species, Sex = sex) |> 
  drop_na() |> 
  count(Year, Island, Species, Sex) |> 
  mutate(Year = factor(Year)) |> 
  rename(Freqency = n) |> 
  ggalluvial::to_lodes_form(key = "Measure", axes = 1:3) 
glimpse(peng_lodes)
```

```{r}
#| label: data_run_alluvial_lf
#| eval: true
#| echo: false 
peng_lodes <- penguins |> 
  select(Year = year, Island = island, 
         Species = species, Sex = sex) |> 
  drop_na() |> 
  count(Year, Island, Species, Sex) |> 
  mutate(Year = factor(Year)) |> 
  rename(Freqency = n) |> 
  ggalluvial::to_lodes_form(key = "Measure", axes = 1:3) 
glimpse(peng_lodes, 50)
```
:::

***

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.70em;"}
1. Create labels
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.70em;"}

2. Map `Measure` to `x`, `Frequency` to `y`, `stratum` to `stratum`, `alluvium` to `alluvium`, and `label` to `stratum`.

3. Add the `geom_alluvium()` and map `Sex` to `fill`  

4. Add the `geom_stratum()` and set the `width` to `0.45`  

5. Add `geom_text()` and set `stat` to `"stratum"`
:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: graph_code_alluvial_lf
#| code-line-numbers: "1-15|1-2|5-9|10|11|12|14-15"
#| eval: false
#| echo: true 
labs_alluvial <- ggtitle(label = "Palmer Penguins", 
    subtitle = "Stratified by year, island and species")

ggp2_alluvial_lf <- ggplot(data = peng_lodes,
  aes(x = Measure,
      y = Freqency,
      stratum = stratum,
      alluvium = alluvium,
      label = stratum)) +
  ggalluvial::geom_alluvium(aes(fill = Sex)) +
  ggalluvial::geom_stratum(width = 0.45) +
  geom_text(stat = "stratum")

ggp2_alluvial_lf + 
  labs_alluvial
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

Convert data to lodes form using `to_lodes_form()` from the `ggalluvial` package.

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_alluvial_lf
#| eval: true
#| echo: false
peng_lodes <- penguins |> 
  select(Year = year, Island = island, 
         Species = species, Sex = sex) |> 
  tidyr::drop_na() |> 
  dplyr::count(Year, Island, Species, Sex) |> 
  dplyr::mutate(Year = factor(Year)) |> 
  dplyr::rename(Freqency = n) |> 
  ggalluvial::to_lodes_form(key = "Measure", axes = 1:3)  
  
labs_alluvial <- ggtitle(label = "Palmer Penguins", 
    subtitle = "Stratified by year, island and species")

ggp2_alluvial_lf <- ggplot(data = peng_lodes,
  aes(x = Measure,
      y = Freqency,
      stratum = stratum,
      alluvium = alluvium,
      label = stratum)) +
  ggalluvial::geom_alluvium(aes(fill = Sex)) +
  ggalluvial::geom_stratum() +
  geom_stratum(width = 0.45) +
  geom_text(stat = "stratum")

ggp2_alluvial_lf + 
  labs_alluvial
```
:::
::::


::::::


# BUMP CHART

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***Should I use this graph?***
:::

<br>

. . .

<br>


Bump charts show how numerical (ranked) values change over time for different categories (or groups). Differences are represented with connecting lines (along the `y` axis) that cover the full timescale (along the `x` axis).

. . .

<br>

We can build bump charts in `ggplot2` with the [`ggbump` package:](https://github.com/davidsjoberg/ggbump)  

```{r inst-ggbump}
#| eval: false
devtools::install_github("davidsjoberg/ggbump")
library(ggbump)
```


## BUMP CHART

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

:::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.70em;"}
We'll use the `fivethirtyeight::tv_hurricanes` data, but slightly restructured and filtered. 
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_bump
#| eval: false
fivethirtyeight::tv_hurricanes |> 
  filter(date > as_date("2017-09-15")) |> 
  pivot_longer(cols = -date, 
    names_to = 'hurricane', 
    values_to = 'value') |> 
  group_by(date) |>
  mutate(rank = rank(value, 
    ties.method = "random")) |> 
  ungroup() -> tidy_hurricanes
glimpse(tidy_hurricanes)
```

```{r}
#| label: data_run_bump
#| eval: true
#| echo: false 
fivethirtyeight::tv_hurricanes |> 
  filter(date > as_date("2017-09-15")) |> 
  pivot_longer(cols = -date, 
    names_to = 'hurricane', 
    values_to = 'value') |> 
  group_by(date) |>
  mutate(rank = rank(value, 
    ties.method = "random")) |> 
  ungroup() -> tidy_hurricanes
glimpse(tidy_hurricanes, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.80em;"}
1. Create labels

2. Map date to the `x`, `rank` to the `y`, and `hurricane` to `color`

3. Add `ggbump::geom_bump()` and set `size` to `2`
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_bump
#| eval: false
#| echo: true
#| code-line-numbers: "1-10|1-4|6|7|8|9|11-12"
labs_bump <- labs(title = "TV News Hurricane Mentions",   
  subtitle = "Between Sep 15-25th, 2017", 
  x = "Date", y = "Rank", 
  color = "Hurricanes")
ggp2_bump <- ggplot(tidy_hurricanes, 
    aes(x = date, 
      y = rank, 
      color = hurricane)) +
    ggbump::geom_bump(size = 2)

ggp2_bump + 
  labs_bump
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

More description of graph...

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_bump
#| eval: true
#| echo: false
# Create labels 
labs_bump <- labs(title = "TV News Hurricane Mentions",   
  subtitle = "Between Sep 15-25th, 2017", 
  x = "Date", y = "Rank", 
  color = "Hurricanes")
# create plot 
ggp2_bump <- ggplot(tidy_hurricanes, 
    aes(date, rank, color = hurricane)) +
    ggbump::geom_bump(size = 2)

ggp2_bump + 
  labs_bump
```
:::
::::

::::::

# Recap

We've covered [`ggplot2` graphs that display]{.fragment} [relationships]{.fragment .highlight-red}
