---
title: "ggplot2 graph gallery"
author: "Statistical Graphs"
format:
  revealjs:
    height: 900
    width: 1600
    code-line-numbers: true
    theme: [night, slides.scss]
    background-transition: fade
    transition: slide
    transition-speed: fast
    highlight-style: ayu-mirage
    
code-link: true
execute:
  echo: true
  freeze: auto
---

```{r setup, include=FALSE}
library(tidyverse)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
library(xml2)
library(reactable)
# options ----
options(
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
# ggplot2 theme ----
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
# funs ----
ds538 <- readr::read_rds("data/ds538.rds")
# movies_data ----
movies_data <- readr::read_rds("data/movies_data.rds")
```

# Load packages

<br>


:::: columns
::: {.column width="49%"}

Data packages:

<br>

::: {style="font-size: 0.80em; color:"}
```{r}
#| eval: true
#| echo: true
#| label: packages-data
library(tidyverse)
# install.packages('fivethirtyeightdata', 
# repos = 'https://fivethirtyeightdata.github.io/drat/', 
# type = 'source')
library(scales)
library(kableExtra)
library(palmerpenguins)
library(fivethirtyeight)
library(ggplot2movies)
```
:::
:::

::: {.column width="2%"}
:::

::: {.column width="49%"}

Graph packages:

<br>

::: {style="font-size: 0.80em; color:"}
```{r}
#| eval: true
#| echo: true
#| label: packages-graphs
# install.packages("devtools")
# devtools::install_github("eclarke/ggbeeswarm")
library(ggbeeswarm)
# devtools::install_github("wilkelab/ggridges")
library(ggridges)
```
:::
:::
::::


# palmerpenguins

<br>

*You can learn more about the `penguins` data on the [package website](https://allisonhorst.github.io/palmerpenguins/)*

<br>

:::: columns
::: {.column width="38%"}
```{r}
#| eval: false
#| echo: true
#| label: penguins
penguins <- palmerpenguins::penguins
glimpse(penguins)
```
:::

::: {.column width="2%"}
:::

::: {.column width="60%"}
```{r}
#| eval: true
#| echo: false
#| label: penguins-glimpse
penguins <- palmerpenguins::penguins
glimpse(penguins, 50)
```
:::
::::

# fivethirtyeight

<br>

*All datasets from the [`fivethirtyeight` package](https://fivethirtyeight-r.netlify.app/) are listed below with descriptions*

<br>

Access them using: 

```{r}
#| label: fivethirtyeight-namespace
#| eval: false
#| echo: true
fivethirtyeight::
```

. . .

```{r}
#| label: fivethirtyeight-kable
#| eval: true
#| echo: false
#| message: false
#| warning: false
kableExtra::kable_material_dark(
  kable_input = knitr::kable(
    head(ds538)
    ), font_size = 25
  )
```

# ggplot2movies

<br>

*We're using `movies_data` (derived version of the [`ggplot2movies::movies`](https://github.com/hadley/ggplot2movies))*

<br>

::: columns
::: {.column width="38%"}
```{r movies_data}
#| eval: false
#| echo: true
#| label: movies_data
#| message: false
#| warning: false
glimpse(movies_data)
```
:::

::: {.column width="2%"}

:::

::: {.column width="60%"}
```{r glimpse-movies_data, echo=FALSE}
#| eval: true
#| echo: false
#| label: movies_data-glimpse
#| message: false
#| warning: false
glimpse(movies_data, 50)
```
:::
:::

# STATISTICAL GRAPHS


# CODE THEN GRAPH (L1)

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Description...

. . .

<br>

More description...


## CODE THEN GRAPH (L2)

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::


::: {style="font-size: 0.80em;"}
The data
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.75em;"}

1. Create the labels

2. 

3. 

4. 
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_
#| code-line-numbers: "1"
#| eval: false
#| echo: true 

```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

More description 

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: graph_create_
#| eval: true
#| echo: false

```
:::
::::


::::::


