---
title: "slide_layout"
subtitle: "ODSC West"
logo: "../img/ODSC_Logo_2020.png"
format: 
  revealjs: 
    height: 900
    width: 1600
    theme: [dark, slides.scss]
    highlight-style: dracula
    transition: fade
    slide-number: true
    chalkboard: true
    scrollable: true
from: markdown+emoji
editor: source
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(faux)
library(palmerpenguins)
penguins <- palmerpenguins::penguins
# the following creates a sample that has 100 observations of 2
# variables, drawn from a population where 
# - X has a mean of 0 and SD of 1 
# - Y has a mean of 20 and SD of 5
# - X correlates with Y with r = 0.75
cor90df <- rnorm_multi(n = 300, 
                  mu = c(0, 20),
                  sd = c(1, 5),
                  r = c(0.90), 
                  varnames = c("X", "Y"),
                  empirical = FALSE)
cor20df <- rnorm_multi(n = 300, 
                  mu = c(0, 20),
                  sd = c(1, 5),
                  r = c(0.20), 
                  varnames = c("X", "Y"),
                  empirical = FALSE)
```


---

2 Column Slide

::: columns
::: {.column width="50%"}
Left Column
:::

::: {.column width="50%"}
Right column
:::
:::

---

3 Column Slide

::: columns
::: {.column width="33%"}
Left column
:::

::: {.column width="33%"}
Middle column
:::

::: {.column width="33%"}
Right column
:::
:::

---

Tabsets

::: panel-tabset
### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`
:::

---

# Question

::: question
1.  What are the drawbacks of this code?

2.  How would you do it instead?
:::


---

# Fragments 

This is an [important sentence!]{.fragment .highlight-red}

---

Column Layout, arbitrary fragment 

::::: {.columns}
:::: {.column width="50%"}
::: {.fragment}

**These appear first**

::: {.incremental}
- Make
- Your 
- List
:::
:::
::::
:::: {.column width="50%"}
::: {.fragment}

**Then this**

::: {style="font-size: 0.52em; color: #ffac00;"}
```{r}
#| echo: fenced
head(mtcars)
```
:::
:::
::::
:::::

---

::: {style="font-size: 1.25em; color: #ffac00;"}
"*The greatest value of a picture is when it forces us to notice what we
never expected to see.*"
:::

. . .

::: {style="font-size: 0.75em; color: #ffac00;"}
```{r}
#| echo: fenced
head(mtcars)
```
:::

---

Tabsets with columns

:::: panel-tabset
### Tab A

Content for `Tab A`

::: columns
::: {.column width="33%"}
Left column
:::

::: {.column width="33%"}
Middle column
:::

::: {.column width="33%"}
Right column
:::
:::

### Tab B

Content for `Tab B`
::::


---

Tabsets with incremental columns

:::::: panel-tabset
### Tab A

::::: {.columns}
:::: {.column width="50%"}
::: {.fragment}

**These appear first**

::: {.incremental}
- Make
- Your 
- List
:::
:::
::::
:::: {.column width="50%"}
::: {.fragment}

**Then this**

::: {style="font-size: 0.52em; color: #ffac00;"}
```{r}
#| echo: fenced
head(mtcars)
```
:::
:::
::::
:::::

### Tab B

::::: {.columns}
:::: {.column width="50%"}
::: {.fragment}

**These appear first**

::: {.incremental}
- Make
- Your 
- List
:::
:::
::::
:::: {.column width="50%"}
::: {.fragment}

**Then this**

::: {style="font-size: 0.52em; color: #ffac00;"}
```{r}
#| echo: fenced
head(mtcars)
```
:::
:::
::::
:::::

::::::

---

# [Code then graph description]

<br>

. . .

::: {style="font-size: 1.25em; color: #09FF00;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Some description

. . .

<br>

More description


## [code then graph]

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}
::: {style="font-size: 0.90em;"}
The data: 
:::
::: {style="font-size: 0.85em;"}
```{r}
#| eval: false
glimpse(data)
```

```{r}
#| eval: true
#| echo: false 
# glimpse(movies_data, 50)
```
:::



:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em;"}
1. *Create the labels*

2. *Step 2* 

3. *Step 3*
:::

::: {style="font-size: 0.85em;"}
```{r}
# Create labels 

# create plot 

```
:::
:::
::::

### Graph

:::: columns
::: {.column width="30%"}
::: {style="font-size: 0.85em;"}
```{r}
#| eval: false
layer + 
  labs
```
:::
:::

::: {.column width="5%"}
:::

::: {.column width="65%"}
```{r}
#| eval: true
#| echo: false
# layer + 
#   labs
```
:::
::::

::::::

# [Graph then code description]

<br>

. . .

::: {style="font-size: 1.25em; color: #09FF00;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Some description

. . .

<br>

More description

## [Graph then code]

:::::: panel-tabset

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

More description of graph...

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_
#| eval: true
#| echo: false

# create graph layers 
# layer + 
#   labs
```
:::
::::

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em;"}
The data: 
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_
#| eval: false
glimpse(data)
```

```{r}
#| label: data_run_
#| eval: true
#| echo: false 
# glimpse(movies_data, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.80em;"}
1. Create the labels

2. Step 2

3. Step 3
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_
#| eval: false
#| echo: true 

# Create labels 

# create plot 

```
:::
:::
::::

::::::

# CODE THEN GRAPH (L1)

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Description...

. . .

<br>

More description...


## CODE THEN GRAPH (L2)

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::


::: {style="font-size: 0.80em;"}
The data
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.75em;"}

1. Create the labels

2. 

3. 

4. 
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_
#| code-line-numbers: "1"
#| eval: false
#| echo: true 

```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

More description 

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: graph_create_
#| eval: true
#| echo: false

```
:::
::::


::::::

# DATA, CODE THEN GRAPH (L1)

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Description...

. . .

<br>

More description...

## DATA, CODE THEN GRAPH (L2)

:::::: panel-tabset

### Data

:::: columns
::: {.column width="35%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.75em;"}
Description of data
:::
:::

::: {.column width="5%"}
:::

::: {.column width="60%"}
::: {style="font-size: 0.75em;"}
```{r}
#| label: data_show_
#| eval: false
glimpse(penguins)
```

```{r}
#| label: data_run_
#| eval: true
#| echo: false 
glimpse(penguins, 50)
```
:::
:::
::::


### Code

:::: columns
::: {.column width="45%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_
#| code-line-numbers: "1"
#| eval: false
#| echo: true 

```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.75em;"}

1. Create the labels

2. 

3. 

4. 
:::
:::

::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::
::: {style="font-size: 0.75em;"}

More description 

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: graph_create_
#| eval: true
#| echo: false

```
:::
::::
::::::

