---
title: "Diverging Bar-graphs (vertical)"
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| message: false
#| warning: false
#| include: false
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
# options ----
options(
  repos = "https://cloud.r-project.org",
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
install.packages("fivethirtyeight")
```



:::: {.callout-tip collapse="false" icon=false}
## Graph info
::: {style="font-size: 1.25em; color: #02577A;"}
**Should I use this graph?**
:::

<br>

```{r}
#| label: full_code_display
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| out-height: '60%'
#| out-width: '60%'
#| fig-align: right
library(fivethirtyeight) 
library(ggplot2)
fivethirtyeight::trump_approval_trend |> 
  filter(subgroup == "All polls") |> 
  mutate(
    month = lubridate::month(modeldate,
                label = TRUE, abbr = TRUE),
    approve = approve_estimate*0.01,
    disapprove = disapprove_estimate*0.01,
    disapprove = disapprove * -1) |> 
  pivot_longer(cols = c(approve, disapprove), 
    names_to = "poll", values_to = "values") |> 
  group_by(month, poll) |> 
    summarise(
      month_avg = mean(values, na.rm = TRUE)
    ) |> 
  ungroup() -> trump_approval_diverg
labs_geom_bar_diverg_vert <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Monthly average percent",
  y = "Month",
  fill = "Estimate")
ggp2_bar_diverg_vert <- ggplot(
  data = trump_approval_diverg,
      aes(x = month_avg, y =  month)) +
  geom_bar(
      aes(fill = poll), 
        stat = "identity", width = .5) + 
  scale_x_continuous(limits = c(-1, 1), 
        labels = scales::percent)
ggp2_bar_diverg_vert + 
  labs_geom_bar_diverg_vert
```

Diverging bar-charts can be arranged vertically, too. 

For vertically arranged bars, we switch the `x` and `y` axis variables.

::::


:::: {.panel-tabset}

### Packages

::: {style="font-size: 0.90em; color: #1e83c8;"}
**PACKAGES:**
:::

::: {style="font-size: 0.85em;"}
Install packages.
:::


::: {style="font-size: 0.75em;"}
```{r}
#| label: pkg_code_vert_diverg_bars
#| eval: true
#| echo: true
#| warning: false
#| message: false
#| results: hide
install.packages("fivethirtyeight")
library(fivethirtyeight) 
library(ggplot2)
```
:::

### Data

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.85em;"}
Create `trump_approval_diverg` from the `trump_approval_trend` dataset in the `fivethirtyeight` package.
:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: data_code_vert_diverg_bars
#| eval: true
#| echo: true
fivethirtyeight::trump_approval_trend |> 
  filter(subgroup == "All polls") |> 
  mutate(
    month = lubridate::month(modeldate,
                label = TRUE, abbr = TRUE),
    approve = approve_estimate*0.01,
    disapprove = disapprove_estimate*0.01,
    disapprove = disapprove * -1) |> 
  pivot_longer(cols = c(approve, disapprove), 
    names_to = "poll", values_to = "values") |> 
  group_by(month, poll) |> 
    summarise(
      month_avg = mean(values, na.rm = TRUE)
    ) |> 
  ungroup() -> trump_approval_diverg
glimpse(trump_approval_diverg)
```
:::
::::

:::: {.panel-tabset}

### Code

::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}

Create labels

Map the `month_avg` to the `x` and `month` to the `y` 

*Inside* `geom_bar()` 

  - map `poll` to `fill`  

  - use `stat = "identity"` and `width = .5`  
  
Add `scale_y_continuous()` to manually set the limits and format the axis with `scales::percent` 

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: code_graph_vert_diverg_bars
#| eval: false
#| echo: true 
#| warning: false
#| message: false
labs_geom_bar_diverg_vert <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Monthly average percent",
  y = "Month",
  fill = "Estimate")
ggp2_bar_diverg_vert <- ggplot(
  data = trump_approval_diverg,
      aes(x = month_avg, y =  month)) +
  geom_bar(
      aes(fill = poll), 
        stat = "identity", width = .5) + 
  scale_x_continuous(limits = c(-1, 1), 
        labels = scales::percent)
ggp2_bar_diverg_vert + 
  labs_geom_bar_diverg_vert
```
:::

### Graph

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

```{r}
#| label: create_graph_vert_diverg_bars
#| eval: true
#| echo: false
#| warning: false
#| message: false
labs_geom_bar_diverg_vert <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Monthly average percent",
  y = "Month",
  fill = "Estimate")
ggp2_bar_diverg_vert <- ggplot(
  data = trump_approval_diverg,
      aes(x = month_avg, y =  month)) +
  geom_bar(
      aes(fill = poll), 
        stat = "identity", width = .5) + 
  scale_x_continuous(limits = c(-1, 1), 
        labels = scales::percent)
ggp2_bar_diverg_vert + 
  labs_geom_bar_diverg_vert
```

::::
