---
title: "ggplot2 graph gallery"
author: "Proportions"
format:
  revealjs:
    height: 900
    width: 1600
    code-line-numbers: true
    theme: [night, slides.scss]
    background-transition: fade
    transition: slide
    transition-speed: fast
    highlight-style: ayu-mirage
    
code-link: true
execute:
  echo: true
  freeze: auto
---

```{r setup, include=FALSE}
library(tidyverse)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
library(xml2)
library(reactable)
# options ----
options(
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
# ggplot2 theme ----
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
# funs ----
ds538 <- readr::read_rds("data/ds538.rds")
# movies_data ----
movies_data <- readr::read_rds("data/movies_data.rds")
```

# Load packages

<br>


:::: columns
::: {.column width="49%"}
Data packages:

<br>

::: {style="font-size: 0.75em; color:"}
```{r}
#| eval: true
#| echo: true
#| label: packages-data
library(tidyverse)
# install.packages('fivethirtyeightdata', 
# repos = 'https://fivethirtyeightdata.github.io/drat/', 
# type = 'source')
library(scales)
library(kableExtra)
library(palmerpenguins)
library(fivethirtyeight)
library(ggplot2movies)
```
:::

:::

::: {.column width="2%"}
:::

::: {.column width="49%"}
Graph packages:

<br>

::: {style="font-size: 0.75em; color:"}
```{r}
#| eval: true
#| echo: true
#| label: packages-graphs
# install.packages("devtools")
# devtools::install_github("kassambara/ggpubr")
library(ggpubr)
# devtools::install_github("liamgilbey/ggwaffle")
library(ggwaffle)
# devtools::install_github("haleyjeppson/ggmosaic")
library(ggmosaic)
# devtools::install_github("wilkox/treemapify")
library(treemapify)
```
:::
:::
::::


# palmerpenguins

<br>

*You can learn more about the `penguins` data on the [package website](https://allisonhorst.github.io/palmerpenguins/)*

<br>

:::: columns
::: {.column width="38%"}
```{r}
#| eval: false
#| echo: true
#| label: penguins
penguins <- palmerpenguins::penguins
glimpse(penguins)
```
:::

::: {.column width="2%"}
:::

::: {.column width="60%"}
```{r}
#| eval: true
#| echo: false
#| label: penguins-glimpse
penguins <- palmerpenguins::penguins
glimpse(penguins, 50)
```
:::
::::

# fivethirtyeight

<br>

*All datasets from the [`fivethirtyeight` package](https://fivethirtyeight-r.netlify.app/) are listed below with descriptions*

<br>

Access them using: 

```{r}
#| label: fivethirtyeight-namespace
#| eval: false
#| echo: true
fivethirtyeight::
```

. . .

```{r}
#| label: fivethirtyeight-kable
#| eval: true
#| echo: false
#| message: false
#| warning: false
kableExtra::kable_material_dark(
  kable_input = knitr::kable(
    head(ds538)
    ), font_size = 25
  )
```

# ggplot2movies

<br>

*We're using `movies_data` (derived version of the [`ggplot2movies::movies`](https://github.com/hadley/ggplot2movies))*

<br>

::: columns
::: {.column width="38%"}
```{r movies_data}
#| eval: false
#| echo: true
#| label: movies_data
#| message: false
#| warning: false
glimpse(movies_data)
```
:::

::: {.column width="2%"}

:::

::: {.column width="60%"}
```{r glimpse-movies_data, echo=FALSE}
#| eval: true
#| echo: false
#| label: movies_data-glimpse
#| message: false
#| warning: false
glimpse(movies_data, 50)
```
:::
:::


# COMPARING PROPORTIONS 

<br>

::: {.fragment fragment-index=1}
Comparing Proportions 
:::

::: {.fragment fragment-index=2}
& Part-to-Whole Relationships
:::

::: {.fragment fragment-index=3}
::: {style="font-size: 1.00em; color: #ffac00;"}
with `ggplot2`
:::
:::

# PIE-CHARTS

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

::: columns
::: {.column width="50%"}
"*In general, pie charts work well when the goal is to emphasize simple fractions, such as one-half, one-third, or one-quarter.*"
:::

::: {.column width="50%"}
"*They also work well when we have very small datasets.*" - Claus O. Wilke, [Fundamentals of Data Visualization](https://clauswilke.com/dataviz/) (2019)
:::
:::

. . .

<br>

Pie-charts are ideal for comparing the proportions of categorical variable values, and we can build pie-charts using the [`ggpubr` package.](https://rpkgs.datanovia.com/ggpubr/)

## PIE-CHARTS

:::::: panel-tabset

### Data

:::: columns
::: {.column width="35%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.75em;"}
Summarise percent `mpaa` in `movies_data`
:::
:::

::: {.column width="5%"}
:::

::: {.column width="60%"}
::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_ggpie
#| eval: false
movie_pie <- movies_data |> 
  dplyr::group_by(mpaa) |> 
  summarise(cnt = n()) |> 
  mutate(
    perc = round(cnt / sum(cnt), 3),
    mpaa = factor(mpaa, 
          levels = c("PG", "PG-13", "R")))
glimpse(movie_pie)
```

```{r}
#| label: data_run_ggpie
#| eval: true
#| echo: false 
movie_pie <- movies_data |> 
  dplyr::group_by(mpaa) |> 
  summarise(cnt = n()) |> 
  mutate(
    perc = round(cnt / sum(cnt), 3),
    mpaa = factor(mpaa, 
          levels = c("PG", "PG-13", "R")))
glimpse(movie_pie, 50)
```
:::
:::
::::


### Code

:::: columns
::: {.column width="45%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_ggpie
#| code-line-numbers: "1-14|1-5|8|9|10|11|13-14"
#| eval: false
#| echo: true 
labs <- paste0(movie_pie$mpaa, " (", 
               (100*movie_pie$perc), "%)")
labs_pie <- labs(
  title = "Percent MPAA ratings for IMDB movies",
  x = "Percent MPAA rating")

ggp2_pie <- ggpubr::ggpie(movie_pie, 
          x = "perc", label = labs, 
          lab.pos = "in", lab.font = "white",
          fill = "mpaa", color = "white") + 
    theme(legend.position = "none")  
    
ggp2_pie + 
  labs_pie
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.75em;"}

1. Create the labels

2. Assign `"perc"` to `x`

3. Assign `labs` to `label` 

4. Assign `"in"` to `lab.pos`

5. Assign `"white"` to `lab.font` and `color`

6. Assign `"mpaa"` to `fill`

7. Remove legend with `theme(legend.position = "none")` 
:::
:::

::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::
::: {style="font-size: 0.75em;"}
*Note the variables in `ggpubr::ggpie()` are assigned in quotes!*
:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: graph_create_ggpie
#| eval: true
#| echo: false
labs <- paste0(movie_pie$mpaa, " (", 
               (100*movie_pie$perc), "%)")
labs_pie <- labs(
  title = "Percent MPAA ratings for IMDB movies",
  x = "Percent MPAA rating")

ggp2_pie <- ggpubr::ggpie(movie_pie, 
          x = "perc", label = labs, 
          lab.pos = "in", lab.font = "white",
          fill = "mpaa", color = "white") + 
    theme(legend.position = "none")  
    
ggp2_pie + 
  labs_pie
```
:::
::::
::::::



# DIVERGING BAR GRAPHS

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

If you have two proportions that contain positive and negative values, consider using diverging bars with `geom_bar()`

## DIVERGING BAR GRAPHS

:::::: panel-tabset

### Data

:::: columns
::: {.column width="35%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.75em;"}
Create `trump_approval_diverg` from the `trump_approval_trend` dataset in the `fivethirtyeight` package.
:::
:::

::: {.column width="5%"}
:::

::: {.column width="60%"}
::: {style="font-size: 0.75em;"}
```{r}
#| label: data_show_diverging_bar
#| eval: false
fivethirtyeight::trump_approval_trend |> 
  filter(subgroup == "All polls") |> 
  mutate(
    month = lubridate::month(modeldate,
                label = TRUE, abbr = TRUE),
    approve = approve_estimate*0.01,
    disapprove = disapprove_estimate*0.01,
    disapprove = disapprove * -1) |> 
  pivot_longer(cols = c(approve, disapprove), 
    names_to = "poll", values_to = "values") |> 
  group_by(month, poll) |> 
    summarise(
      month_avg = mean(values, na.rm = TRUE)
    ) |> 
  ungroup() -> trump_approval_diverg
glimpse(trump_approval_diverg)
```

```{r}
#| label: data_run_diverging_bar
#| eval: true
#| echo: false 
fivethirtyeight::trump_approval_trend |> 
  filter(subgroup == "All polls") |> 
  mutate(
    month = lubridate::month(modeldate,
                label = TRUE, abbr = TRUE),
    approve = approve_estimate*0.01,
    disapprove = disapprove_estimate*0.01,
    disapprove = disapprove * -1) |> 
  pivot_longer(cols = c(approve, disapprove), 
    names_to = "poll", values_to = "values") |> 
  group_by(month, poll) |> 
    summarise(
      month_avg = mean(values, na.rm = TRUE)
    ) |> 
  ungroup() -> trump_approval_diverg
glimpse(trump_approval_diverg, 50)
```
:::
:::
::::


### Code

:::: columns
::: {.column width="45%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_diverging_bar
#| code-line-numbers: "1-16|1-6|9|10-11|12-13|15-16"
#| eval: false
#| echo: true 
labs_geom_bar_diverg <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Month",
  y = "Monthly average percent",
  fill = "Estimate")
ggp2_bars_diverg <- ggplot(
  data = trump_approval_diverg, 
    aes(x = month, y = month_avg)) +
  geom_bar(aes(fill = poll),
    stat = "identity", width = .5) + 
  scale_y_continuous(limits = c(-1, 1), 
    labels = scales::percent)

ggp2_bars_diverg + 
  labs_geom_bar_diverg
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.80em;"}
1. Create the labels

2. Map the `month` to the `x` and `month_avg` to the `y`  

3. *Inside* `geom_bar()`    
   - map `poll` to `fill`  
   - use `stat = "identity"` and `width = .5`  
  
4. Add `scale_y_continuous()` to manually set the limits and format the axis with `scales::percent`  
:::
:::

::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::
::: {style="font-size: 0.75em;"}

Diverging bars display the bars above and below zero (or some reference value)

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: graph_create_diverging_bar
#| eval: true
#| echo: false
labs_geom_bar_diverg <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Month",
  y = "Monthly average percent",
  fill = "Estimate")
ggp2_bars_diverg <- ggplot(
  data = trump_approval_diverg, 
    aes(x = month, y = month_avg)) +
  geom_bar(aes(fill = poll),
    stat = "identity", width = .5) + 
  scale_y_continuous(limits = c(-1, 1), 
    labels = scales::percent)

ggp2_bars_diverg + 
  labs_geom_bar_diverg
```
:::
::::
::::::

# DIVERGING BAR GRAPHS (VERTICAL)

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Diverging bar-charts can be arranged vertically, too. 

. . . 

<br>

For vertically arranged bars, we switch the `x` and `y` axis variables.

## DIVERGING BAR GRAPHS (VERTICAL)

:::::: panel-tabset

### Data

:::: columns
::: {.column width="35%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.75em;"}
Create `trump_approval_diverg` from the `trump_approval_trend` dataset in the `fivethirtyeight` package.
:::
:::

::: {.column width="5%"}
:::

::: {.column width="60%"}
::: {style="font-size: 0.75em;"}
```{r}
#| label: data_show_diverging_bar_vert
#| eval: false
fivethirtyeight::trump_approval_trend |> 
  filter(subgroup == "All polls") |> 
  mutate(
    month = lubridate::month(modeldate,
                label = TRUE, abbr = TRUE),
    approve = approve_estimate*0.01,
    disapprove = disapprove_estimate*0.01,
    disapprove = disapprove * -1) |> 
  pivot_longer(cols = c(approve, disapprove), 
    names_to = "poll", values_to = "values") |> 
  group_by(month, poll) |> 
    summarise(
      month_avg = mean(values, na.rm = TRUE)
    ) |> 
  ungroup() -> trump_approval_diverg
glimpse(trump_approval_diverg)
```

```{r}
#| label: data_run_diverging_bar_vert
#| eval: true
#| echo: false 
fivethirtyeight::trump_approval_trend |> 
  filter(subgroup == "All polls") |> 
  mutate(
    month = lubridate::month(modeldate,
                label = TRUE, abbr = TRUE),
    approve = approve_estimate*0.01,
    disapprove = disapprove_estimate*0.01,
    disapprove = disapprove * -1) |> 
  pivot_longer(cols = c(approve, disapprove), 
    names_to = "poll", values_to = "values") |> 
  group_by(month, poll) |> 
    summarise(
      month_avg = mean(values, na.rm = TRUE)
    ) |> 
  ungroup() -> trump_approval_diverg
glimpse(trump_approval_diverg, 50)
```
:::
:::
::::


### Code

:::: columns
::: {.column width="45%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_diverging_bar_vert
#| code-line-numbers: "1-16|1-6|9|10-12|13-14|15-16"
#| eval: false
#| echo: true 
labs_geom_bar_diverg_vert <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Monthly average percent",
  y = "Month",
  fill = "Estimate")
ggp2_bar_diverg_vert <- ggplot(
  data = trump_approval_diverg,
      aes(x = month_avg, y =  month)) +
  geom_bar(
      aes(fill = poll), 
        stat = "identity", width = .5) + 
  scale_x_continuous(limits = c(-1, 1), 
        labels = scales::percent)
ggp2_bar_diverg_vert + 
  labs_geom_bar_diverg_vert
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.75em;"}
1. Create the labels

2. Map the `month_avg` to the `x` and `month` to the `y` 

3. *Inside* `geom_bar()`    
   - map `poll` to `fill`  
   - use `stat = "identity"` and `width = .5`  
  
4. Add `scale_y_continuous()` to manually set the limits and format the axis with `scales::percent` 
:::
:::

::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::
::: {style="font-size: 0.75em;"}

Diverging bar-graphs can also be arranged vertically across a reference value

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: graph_create_diverging_bar_vert
#| eval: true
#| echo: false
labs_geom_bar_diverg_vert <- labs(
  title = "Trump Approval Ratings",
  subtitle = "From 'How Popular is Donald Trump'",
  x = "Monthly average percent",
  y = "Month",
  fill = "Estimate")
ggp2_bar_diverg_vert <- ggplot(
  data = trump_approval_diverg,
      aes(x = month_avg, y =  month)) +
  geom_bar(
      aes(fill = poll), 
        stat = "identity", width = .5) + 
  scale_x_continuous(limits = c(-1, 1), 
        labels = scales::percent)
ggp2_bar_diverg_vert + 
  labs_geom_bar_diverg_vert
```
:::
::::
::::::



# STACKED (OR FILLED) DENSITY GRAPHS

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Density graphs are typically used to visualize the distribution of a single variable,

. . .

<br>

but stacked density graphs are great for visualizing how proportions vary across numeric (continuous) variables.

## STACKED (OR FILLED) DENSITY GRAPHS

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
Remove missing `sex` from the `penguins` data
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_fill_density
#| eval: false
peng_density <- filter(penguins, !is.na(sex))
glimpse(peng_density)
```

```{r}
#| label: data_run_fill_density
#| eval: true
#| echo: false 
peng_density <- filter(penguins, !is.na(sex))
glimpse(peng_density, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::
::: {style="font-size: 0.80em;"}
1. Create the labels

2. Map the `flipper_length_mm` to the `x` and add  `after_stat(count)` 

3. Map `sex` to `fill`  

3. *Inside* the `geom_density()` function, set `position` to `"fill"`

:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: graph_code_fill_density
#| code-line-numbers: "1-10|1-4|6|7|8|9|10-11"
#| eval: false
#| echo: true 
labs_fill_density <- labs(
  title = "Adult foraging penguins",
  x = "Flipper length (millimeters)",
  fill = "Penguin sex (female, male)")
ggp2_fill_density <- ggplot(data = peng_density, 
       aes(x = flipper_length_mm, 
           after_stat(count),
          fill = sex)) +
      geom_density(position = "fill") 
ggp2_fill_density + 
  labs_fill_density
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

[*You can use `position = "fill"` to produce a conditional density estimate*](https://ggplot2.tidyverse.org/reference/geom_density.html#ref-examples)

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_fill_density
#| eval: true
#| echo: false
peng_density <- filter(penguins, !is.na(sex))
labs_fill_density <- labs(
  title = "Adult foraging penguins",
  x = "Flipper length (millimeters)",
  fill = "Penguin sex (female, male)")
ggp2_fill_density <- ggplot(data = peng_density, 
       aes(x = flipper_length_mm, 
          fill = sex)) +
      geom_density(position = "fill") 
ggp2_fill_density + 
  labs_fill_density
```
:::
::::


::::::

# MOSAIC PLOT

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

A mosaic plot is similar to a stacked bar-graph, but instead of only relying on height and color to display the relative amount for each value, mosaic plots also use width

. . .

<br>

We can build mosaic plots using the [`ggmosaic` package.](https://haleyjeppson.github.io/ggmosaic/)


## MOSAIC PLOT

:::::: panel-tabset

### Code

:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
The `fivethirtyeight::flying` data, after removing the missing values from `baby` and `unruly_child`. 
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_mosaic
#| eval: false

flying <- fivethirtyeight::flying
fly_mosaic <- filter(flying, 
              !is.na(baby) & !is.na(unruly_child)) |> 
              select(baby, unruly_child)
glimpse(fly_mosaic)
```

```{r}
#| label: data_run_mosaic
#| eval: true
#| echo: false 

flying <- fivethirtyeight::flying
fly_mosaic <- filter(flying, 
              !is.na(baby) & !is.na(unruly_child)) |> 
              select(baby, unruly_child)
                
glimpse(fly_mosaic, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::
::: {style="font-size: 0.70em;"}
1. Create the labels

2. Map the `product()` of `unruly_child` and `baby` to the `x` axis

3. Map `unruly_child` to `fill`

4. Move the `legend` to the top of the graph with `theme(legend.position = "top")`
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: mosaic
#| code-line-numbers: "1-13|1-6|9|10|11|12-13"
#| eval: false
#| echo: true 

labs_mosaic <- labs(
  title = "In general...", 
  subtitle = "...is it rude to...",
  x = "... bring a baby on a plane?",
  y = "..,knowingly bring unruly children on a plane?",
  fill = "Responses") 
ggp2_mosaic <- ggplot(data = fly_mosaic) +
  ggmosaic::geom_mosaic(
    aes(x = product(unruly_child, baby), 
                  fill = unruly_child)) + 
  theme(legend.position = "top")
ggp2_mosaic + 
  labs_mosaic
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

It's a good idea to adjust the `fig-height` and `fig-width` of your graph:

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_mosaic
#| eval: true
#| echo: false
#| fig-height: 7.5
#| fig-width: 9.25
#| fig-dpi: 400

flying <- fivethirtyeight::flying
fly_mosaic <- filter(flying, !is.na(baby) &
                 !is.na(unruly_child))

labs_mosaic <- labs(
  title = "In general...", 
  subtitle = "...is it rude to...",
  x = "... bring a baby on a plane?",
  y = "..,knowingly bring unruly children on a plane?",
  fill = "Responses") 
ggp2_mosaic <- ggplot(data = fly_mosaic) +
  ggmosaic::geom_mosaic(
    aes(x = product(unruly_child, baby), 
                  fill = unruly_child)) + 
  theme(legend.position = "top")
ggp2_mosaic + 
  labs_mosaic
```
:::
::::


::::::


# TREEMAPS

<br>

. . .

::: {style="font-size: 1.25em; color: #ffd500;"}
***When would I use this graph?***
:::

<br>

. . .

<br>

Treemaps display how numerical hierarchical values make up a whole in a rectangular layout.

. . .

<br>

We'll build a treemap using the [`treemapify` package.](http://wilkox.org/treemapify/) 

## TREEMAPS

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
Filter the missing values from `sex`, group the data by `species`, `island`, and `sex`, then count the `species` and `island` (then `ungroup()`).
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_treemaps
#| eval: false
treemap_peng <- penguins |> 
                  filter(!is.na(sex)) |> 
                  group_by(species, island, sex) |>
  count(species, island) |> 
  ungroup()
glimpse(treemap_peng)
```

```{r}
#| label: data_run_treemaps
#| eval: true
#| echo: false 
treemap_peng <- penguins |> 
                  filter(!is.na(sex)) |> 
                  group_by(species, island, sex) |>
  count(species, island) |> 
  ungroup()
glimpse(treemap_peng, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.80em;"}
1. Create the labels

2. Map the `n` to `area`, `sex` to `fill`, `species` to `label`, and `island` to `subgroup`
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: treemaps
#| code-line-numbers: "1-12|1-2|4|5|6|7|8|11-12"
#| eval: false
#| echo: true 
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap() 
ggp2_treemap + 
  labs_treemap
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

This layout is often referred to as "*squarified*", and it represents 100% of the total values

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_treemaps
#| eval: true
#| echo: false
treemap_peng <- penguins |> 
                  filter(!is.na(sex)) |> 
                  group_by(species, island, sex) |>
  count(species, island) |> 
  ungroup()
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap() 
ggp2_treemap + 
  labs_treemap
```
:::
::::


::::::

## MORE TREEMAPS

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
Filter the missing values from `sex`, group the data by `species`, `island`, and `sex`, then count the `species` and `island` (then `ungroup()`).
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_ggp2_treemap_sgb
#| eval: false
treemap_peng <- penguins |> 
          filter(!is.na(sex)) |> 
          group_by(species, island, sex) |>
          count(species, island) |> 
          ungroup()
glimpse(treemap_peng)
```

```{r}
#| label: data_run_ggp2_treemap_sgb
#| eval: true
#| echo: false 
treemap_peng <- penguins |> 
          filter(!is.na(sex)) |> 
          group_by(species, island, sex) |>
          count(species, island) |> 
          ungroup()
glimpse(treemap_peng, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.80em;"}
1. Add the borders with `geom_treemap_subgroup_border()`
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: ggp2_treemap_sgb
#| code-line-numbers: "|10"
#| eval: false
#| echo: true 
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap()
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_treemap_sgb + 
  labs_treemap
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

Add border lines to the subgroups 

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_ggp2_treemap_sgb
#| eval: true
#| echo: false
treemap_peng <- penguins |> 
          filter(!is.na(sex)) |> 
          group_by(species, island, sex) |>
          count(species, island) |> 
          ungroup()
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap()
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_treemap_sgb + 
  labs_treemap
```
:::
::::


::::::


## EVEN MORE TREEMAPS

:::::: panel-tabset

### Code


:::: columns
::: {.column width="45%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.80em;"}
Filter the missing values from `sex`, group the data by `species`, `island`, and `sex`, then count the `species` and `island` (then `ungroup()`).
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: data_show_ggp2_tmap_sgb_txt
#| eval: false
treemap_peng <- penguins |> 
          filter(!is.na(sex)) |> 
          group_by(species, island, sex) |>
          count(species, island) |> 
          ungroup()
glimpse(treemap_peng)
```

```{r}
#| label: data_run_ggp2_tmap_sgb_txt
#| eval: true
#| echo: false 
treemap_peng <- penguins |> 
          filter(!is.na(sex)) |> 
          group_by(species, island, sex) |>
          count(species, island) |> 
          ungroup()
glimpse(treemap_peng, 50)
```
:::

:::

::: {.column width="5%"}
:::

::: {.column width="50%"}

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.80em;"}
1. Include labels for subgroup with `geom_treemap_subgroup_text()` (see full list of arguments [here](http://wilkox.org/treemapify/))
:::

::: {style="font-size: 0.85em;"}
```{r}
#| label: ggp2_tmap_sgb_txt
#| code-line-numbers: "1-2|3-11|5|6|7|8|9|10|11|12-14"
#| eval: false
#| echo: true 
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_tmap_sgb_txt <- 
  treemapify::geom_treemap_subgroup_text(
         place = "center", 
         grow = TRUE, 
         alpha = 0.9, 
         color = "white",
         fontface = "bold",
         family = "sans",
         min.size = 0)
ggp2_treemap_sgb + 
  ggp2_tmap_sgb_txt + 
  labs_treemap
```
:::
:::
::::

### Graph

:::: columns
::: {.column width="20%"}
::: {style="font-size: 0.75em;"}

Add text to the treemap sub-groups

:::
:::

::: {.column width="5%"}
:::

::: {.column width="75%"}

```{r}
#| label: create_ggp2_tmap_sgb_txt
#| eval: true
#| echo: false
treemap_peng <- penguins |> 
          filter(!is.na(sex)) |> 
          group_by(species, island, sex) |>
          count(species, island) |> 
          ungroup()
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_tmap_sgb_txt <- 
  treemapify::geom_treemap_subgroup_text(
         place = "center", 
         grow = TRUE, 
         alpha = 0.9, 
         color = "white",
         fontface = "bold",
         family = "sans",
         min.size = 0)
ggp2_treemap_sgb + 
  ggp2_tmap_sgb_txt + 
  labs_treemap
```
:::
::::


::::::

# Recap

We've covered [`ggplot2` graphs that display]{.fragment} [proportions]{.fragment .highlight-red}
