---
title: "Side-to-side (`'dodge'`) bar-graphs"
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| message: false
#| warning: false
#| include: false
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
# options ----
options(
  repos = "https://cloud.r-project.org",
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
install.packages("ggplot2movies")
install.packages("palmerpenguins")
```



:::: {.callout-tip collapse="false"}
## Graph info
::: {style="font-size: 1.25em; color: #38B44A;"}
**When would I use this graph?**
:::

<br>

```{r}
#| label: full_code_display
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| out-height: '60%'
#| out-width: '60%'
#| fig-align: right
library(palmerpenguins) 
library(ggplot2)
penguins_dodge <- filter(penguins,
                    !is.na(sex) & !is.na(species))
labs_bar_dodge <- labs(
  title = "Adult foraging penguins",
  subtitle = "position = 'dodge'",
  x = "Penguin Species",
  fill = "Penguin Sex")

ggp2_bar_dodge <- ggplot(data = penguins_dodge,
                    aes(x = species,
                      fill = sex)) +
                    geom_bar(position = "dodge")
ggp2_bar_dodge +
  labs_bar_dodge
```

To compare amounts using bar size (length or height) in a side-to-side display, we can set the position in `geom_bar()` to `"dodge"` or `"dodge2"`

::::


:::: {.panel-tabset}

### Packages

::: {style="font-size: 0.90em; color: #1e83c8;"}
**PACKAGES:**
:::

::: {style="font-size: 0.85em;"}
Install packages.
:::


::: {style="font-size: 0.75em;"}
```{r}
#| label: pkg_code_dodge
#| eval: true
#| echo: true
#| warning: false
#| message: false
#| results: hide
install.packages("palmerpenguins")
library(palmerpenguins) 
library(ggplot2)
```
:::

### Data

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.85em;"}
Remove any missing values from `sex` and `species` in the `penguins` data.
:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: data_code_dodge
#| eval: true
#| echo: true
penguins_dodge <- filter(penguins,
                    !is.na(sex) & !is.na(species))
glimpse(penguins_dodge)
```
:::
::::

:::: {.panel-tabset}

### Code

::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}

Create the labels

Map `species` to the `x` and `sex` to `fill`

Inside the `geom_bar()` function, set `position` to `"dodge"`

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: code_graph_dodge
#| eval: false
#| echo: true 
#| warning: false
#| message: false
labs_bar_dodge <- labs(
  title = "Adult foraging penguins",
  subtitle = "position = 'dodge'",
  x = "Penguin Species",
  fill = "Penguin Sex")

ggp2_bar_dodge <- ggplot(data = penguins_dodge,
                    aes(x = species,
                      fill = sex)) +
                    geom_bar(position = "dodge")
ggp2_bar_dodge +
  labs_bar_dodge
```
:::

### Graph

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

```{r}
#| label: create_graph_dodge
#| eval: true
#| echo: false
#| warning: false
#| message: false
labs_bar_dodge <- labs(
  title = "Adult foraging penguins",
  subtitle = "position = 'dodge'",
  x = "Penguin Species",
  fill = "Penguin Sex")

ggp2_bar_dodge <- ggplot(data = penguins_dodge,
                    aes(x = species,
                      fill = sex)) +
                    geom_bar(position = "dodge")
ggp2_bar_dodge +
  labs_bar_dodge
```

::::