---
title: "Mosaic Plots"
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| message: false
#| warning: false
#| include: false
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
# options ----
options(
  repos = "https://cloud.r-project.org",
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
install.packages("fivethirtyeight")
devtools::install_github("haleyjeppson/ggmosaic")
library()
```



:::: {.callout-tip collapse="false"}
## Graph info
::: {style="font-size: 1.25em; color: #38B44A;"}
**When would I use this graph?**
:::

<br>

```{r}
#| label: full_code_display
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| out-height: '60%'
#| out-width: '60%'
#| fig-align: right
library(fivethirtyeight) 
library(ggmosaic)
library(ggplot2) 
flying <- fivethirtyeight::flying
fly_mosaic <- filter(flying, 
              !is.na(baby) & !is.na(unruly_child)) |> 
              select(baby, unruly_child)
labs_mosaic <- labs(
      title = "In general...", 
      subtitle = "...is it rude to...",
      x = "... bring a baby on a plane?",
      y = "..,knowingly bring unruly children on a plane?",
      fill = "Responses") 
ggp2_mosaic <- ggplot(data = fly_mosaic) +
  geom_mosaic(aes(x = product(unruly_child, baby), 
      fill = baby)) +
  theme_mosaic()
ggp2_mosaic + 
    labs_mosaic
```

A mosaic plot is similar to a stacked bar-graph, but instead of only relying on height and color to display the relative amount for each value, mosaic plots also use width.

We can build mosaic plots using the [`ggmosaic` package.](https://haleyjeppson.github.io/ggmosaic/)

::::


:::: {.panel-tabset}

### Packages

::: {style="font-size: 0.90em; color: #1e83c8;"}
**PACKAGES:**
:::

::: {style="font-size: 0.85em;"}
Install packages.
:::


::: {style="font-size: 0.75em;"}
```{r}
#| label: pkg_code_
#| eval: true
#| echo: true
#| warning: false
#| message: false
#| results: hide
install.packages("fivethirtyeight")
library(fivethirtyeight) 
devtools::install_github("haleyjeppson/ggmosaic")
library(ggmosaic)
library(ggplot2)
```
:::

### Data

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.85em;"}
Description of data
:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: data_code_
#| eval: true
#| echo: true
flying <- fivethirtyeight::flying
fly_mosaic <- filter(flying, 
              !is.na(baby) & !is.na(unruly_child)) |> 
              select(baby, unruly_child)
glimpse(fly_mosaic)
```
:::
::::

:::: {.panel-tabset}

### Code

::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}

Create the labels

Map the `product()` of `unruly_child` and `baby` to the `x` axis

Map `baby` to `fill`

Add `theme_mosaic()`

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: code_graph_
#| eval: false
#| echo: true 
#| warning: false
#| message: false
#| fig-height: 7
#| fig-width: 7
labs_mosaic <- labs(
      title = "In general...", 
      subtitle = "...is it rude to...",
      x = "... bring a baby on a plane?",
      y = "..,knowingly bring unruly children on a plane?",
      fill = "Responses") 
ggp2_mosaic <- ggplot(data = fly_mosaic) +
  geom_mosaic(aes(x = product(unruly_child, baby), 
      fill = baby)) +
  theme_mosaic()
ggp2_mosaic + 
    labs_mosaic
```
:::

### Graph

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

::: {style="font-size: 0.85em;"}
*It's a good idea to adjust the `fig-height` and `fig-width` of your graph:*
:::

```{r}
#| label: create_graph_
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| fig-height: 7
#| fig-width: 7
labs_mosaic <- labs(
      title = "In general...", 
      subtitle = "...is it rude to...",
      x = "... bring a baby on a plane?",
      y = "..,knowingly bring unruly children on a plane?",
      fill = "Responses") 
ggp2_mosaic <- ggplot(data = fly_mosaic) +
  geom_mosaic(aes(x = product(unruly_child, baby), 
      fill = baby)) +
  theme_mosaic()
ggp2_mosaic + 
    labs_mosaic
```

::::