---
title: "Treemaps"
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| message: false
#| warning: false
#| include: false
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(kableExtra)
library(colorblindr)
library(downlit)
# options ----
options(
  repos = "https://cloud.r-project.org",
  dplyr.print_min = 6, 
  dplyr.print_max = 6, 
  scipen = 9999)
ggplot2::theme_set(ggplot2::theme_minimal(base_size = 18))
devtools::install_github("wilkox/treemapify")
install.packages("palmerpenguins")
```



:::: {.callout-tip collapse="false"}
## Graph info
::: {style="font-size: 1.25em; color: #38B44A;"}
**When would I use this graph?**
:::

<br>

```{r}
#| label: full_code_display
#| eval: true
#| echo: false
#| warning: false
#| message: false
#| out-height: '60%'
#| out-width: '60%'
#| fig-align: right
library(treemapify) 
library(palmerpenguins)
library(ggplot2)
treemap_peng <- penguins |> 
                  filter(!is.na(sex)) |> 
                  group_by(species, island, sex) |>
  count(species, island) |> 
  ungroup()
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
# geom_treemap
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap() 
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
# geom_treemap_subgroup_border
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap()
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
# geom_treemap_subgroup_text
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_tmap_sgb_txt <- 
  treemapify::geom_treemap_subgroup_text(
         place = "center", 
         grow = TRUE, 
         alpha = 0.9, 
         color = "white",
         fontface = "bold",
         family = "sans",
         min.size = 0)
ggp2_treemap_sgb + 
  ggp2_tmap_sgb_txt + 
  labs_treemap
```

Treemaps display how numerical hierarchical values make up a whole in a rectangular layout.

We'll build a treemap using the [`treemapify` package.](http://wilkox.org/treemapify/) 

::::


:::: {.panel-tabset}

### Packages

::: {style="font-size: 0.90em; color: #1e83c8;"}
**PACKAGES:**
:::

::: {style="font-size: 0.85em;"}
Install packages.
:::


::: {style="font-size: 0.75em;"}
```{r}
#| label: pkg_code_treemap
#| eval: true
#| echo: true
#| warning: false
#| message: false
#| results: hide
devtools::install_github("wilkox/treemapify")
install.packages("palmerpenguins")
library(treemapify) 
library(palmerpenguins)
library(ggplot2)
```
:::

### Data

::: {style="font-size: 0.90em; color: #1e83c8;"}
**DATA:**
:::

::: {style="font-size: 0.85em;"}
Filter the missing values from `sex`, group the data by `species`, `island`, and `sex`, then count the `species` and `island` (then `ungroup()`).
:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: data_code_treemap
#| eval: true
#| echo: true
treemap_peng <- penguins |> 
                  filter(!is.na(sex)) |> 
                  group_by(species, island, sex) |>
  count(species, island) |> 
  ungroup()
glimpse(treemap_peng)
```
:::
::::

:::: {.panel-tabset}

### Code

::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}

Create the labels

Map the `n` to `area`, `sex` to `fill`, `species` to `label`, and `island` to `subgroup`

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: code_graph_treemap
#| eval: false
#| echo: true 
#| warning: false
#| message: false
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap() 
ggp2_treemap + 
  labs_treemap
```
:::

### Graph

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

```{r}
#| label: create_graph_treemap
#| eval: true
#| echo: false
#| warning: false
#| message: false
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap() 
ggp2_treemap + 
  labs_treemap
```

::::

### MORE TREEMAPS

:::: {.panel-tabset}

### Code

::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}

Add the borders with `geom_treemap_subgroup_border()`

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: code_graph_treemap_sgb
#| eval: false
#| echo: true 
#| warning: false
#| message: false
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap()
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_treemap_sgb + 
  labs_treemap
```
:::

### Graph

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

```{r}
#| label: create_graph_treemap_sgb
#| eval: true
#| echo: false
#| warning: false
#| message: false
labs_treemap <- labs(
  title = "Species, island, and sex of adult penguins")
ggp2_treemap <- ggplot(treemap_peng, 
       aes(area = n, 
           fill = sex, 
           label = species,
           subgroup = island)) +
       treemapify::geom_treemap()
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_treemap_sgb + 
  labs_treemap
```

::::

### EVEN MORE TREEMAPS

:::: {.panel-tabset}

### Code

::: {style="font-size: 0.90em; color: #1e83c8;"}
**CODE:**
:::

::: {style="font-size: 0.85em;"}

Include labels for subgroup with `geom_treemap_subgroup_text()` (see full list of arguments [here](http://wilkox.org/treemapify/))

:::

::: {style="font-size: 0.75em;"}
```{r}
#| label: code_graph_tmap_sgb_txt
#| eval: false
#| echo: true 
#| warning: false
#| message: false
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_tmap_sgb_txt <- 
  treemapify::geom_treemap_subgroup_text(
         place = "center", 
         grow = TRUE, 
         alpha = 0.9, 
         color = "white",
         fontface = "bold",
         family = "sans",
         min.size = 0)
ggp2_treemap_sgb + 
  ggp2_tmap_sgb_txt + 
  labs_treemap
```
:::

### Graph

::: {style="font-size: 0.90em; color: #1e83c8;"}
**GRAPH:**
:::

```{r}
#| label: create_graph_tmap_sgb_txt
#| eval: true
#| echo: false
#| warning: false
#| message: false
ggp2_treemap_sgb <- ggp2_treemap + 
       treemapify::geom_treemap_subgroup_border()
ggp2_tmap_sgb_txt <- 
  treemapify::geom_treemap_subgroup_text(
         place = "center", 
         grow = TRUE, 
         alpha = 0.9, 
         color = "white",
         fontface = "bold",
         family = "sans",
         min.size = 0)
ggp2_treemap_sgb + 
  ggp2_tmap_sgb_txt + 
  labs_treemap
```

::::